SIR-RL: Reinforcement Learning for Optimized Policy Control during Epidemiological Outbreaks in Emerging Market and Developing Economies

### 2024-03-31 paper_draft/main.tex
fixes in 2.6
bib without doi
APA style references

This \cref{fig:interpolated_nu_varying_with_time_IND} shows us that the $\nu$ coincides with the actual of data of when the vaccination drive was first launched in India~\cite{UnicefCovidVaccine,PIBCovidVaccine,WikipediaCovidVaccine}. Therefore, using these values we finally, recompute $\beta_{optimal}$ and $\gamma_{optimal}$ by supplying them into the equations for the SIR Model with lockdown and time-varying $\nu$.

@@

\subsection{Modelling Normalized GDP with Stringency}
Now, that a relation between $\beta$ and $s(t)$ is set up, it must be investigated how stringency index affects the normalized gross domestic product (GDP)~\cite{OECDNormalizedGDP,OECDNormalizedGDP2}. To do this a polynomial equation of the third degree is fitted to the data points $f(x) = a x^3 + b x^2 + c x + d = y$, here, $x$ is the stringency ($s$), and $y$ the normalized GDP, and we minimize the squared error to find the values of coefficients $a, b, c, d$. For India after fitting a 3 degree polynomial, the following equation is obtained:
\begin{equation}
    \begin{split}
      \textrm{normalized\_GDP} = -5.96640236 \times 10^{-5} s^{3} + 6.65064332 \times 10^{-3} s^{2} - 2.23109924 \times 10^{-1} s^{1} \\
    + 1.01357226 \times 10^{2}
    \end{split}
    \label{eq:gdp_modelled_with_stringency_IND}
\end{equation}

@@

\subsection{Code}
We used stable-baseline3~\cite{JMLR:v22:20-1364}, Pytorch~\cite{paszke2019pytorch}, Scipy~\cite{Virtanen_2020}, Pandas, Matplotlib, in Python~\cite{ScientificPython}.
Code: \url{https://github.com/psymbio/sir_rl}
% \bibliographystyle{plain}
\bibliography{sample}
\end{document}

>>>>

% This \cref{fig:interpolated_nu_varying_with_time_IND} shows us that the $\nu$ coincides with the actual of data of when the vaccination drive was first launched in India~\cite{UnicefCovidVaccine,PIBCovidVaccine,WikipediaCovidVaccine}. Therefore, using these values we finally, recompute $\beta_{optimal}$ and $\gamma_{optimal}$ by supplying them into the equations for the SIR Model with lockdown and time-varying $\nu$.
This \cref{fig:interpolated_nu_varying_with_time_IND} shows us that the $\nu$ coincides with the actual of data of when the vaccination drive was first launched in India~\cite{UnicefCovidVaccine}. Therefore, using these values we finally, recompute $\beta_{optimal}$ and $\gamma_{optimal}$ by supplying them into the equations for the SIR Model with lockdown and time-varying $\nu$.

@@

\subsection{Modelling Normalized GDP with Stringency}
Now, that a relation between $\beta$ and $s(t)$ is set up, it must be investigated how stringency index affects the normalized gross domestic product (GDP)~\cite{OECDNormalizedGDP,OECDNormalizedGDP2}. To do this a polynomial equation of the third degree is fitted to the data points $f(x) = a x^3 + b x^2 + c x + d = y$, here, $x$ is the stringency ($s$), and $y$ the normalized GDP, and we minimize the squared error to find the values of coefficients $a, b, c, d$. For India after fitting a 3 degree polynomial, the following equation is obtained:
\begin{equation}
    \begin{split}
      \textrm{normalized\_GDP} = -5.96640236 \times 10^{-5} s^{3} + 6.65064332 \times 10^{-3} s^{2} - 2.23109924 \times 10^{-1} s \\
    + 1.01357226 \times 10^{2}
    \end{split}
    \label{eq:gdp_modelled_with_stringency_IND}
\end{equation}

@@

\subsection{Code}
We used stable-baseline3~\cite{JMLR:v22:20-1364}, Pytorch~\cite{paszke2019pytorch}, Scipy~\cite{Virtanen_2020}, Pandas, Matplotlib, in Python~\cite{ScientificPython}.
Code: \url{https://github.com/psymbio/sir_rl}
% \bibliographystyle{plain}
% \bibliographystyle{apalike}
\bibliography{newsample}
\end{document}
